---
title: "Erdt_Moritz_AssignmentV"
subtitle: "Data Science Project Management"
author: "Moritz Erdt"
date: "16.02.2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set (echo = TRUE)
library(httr)
library(rlist)
library(jsonlite)
library(tidyverse)
library(maps)

source("C:/Users/morit/Google Drive/Master/studium/01_WS2021/data-science-project-management/tutorial/05-assignment/api_key.R")
```

## General Note

This is the solution for the fifth assignment in Data Science Project 
Management. It has been written by myself in collaboration/exchange with Jan 
Besler (Student ID 5629079).

## 1. Setting up a new GitHub repository
A public GitHub repository has been created to document the solution properly.
I can be accessed [here](https://github.com/MoEPunkt/05-assignment.git).

## 2. Getting to know the API

This assignment deals with the API of Ticketmaster.com. 
The rules allow for 5000 API calls per day with a rate limitation of 5 requests 
per second.
Further, the received API key is sourced into this script.

## 3. Interacting with the API - the basics

The used R-packages to deal with APIs are `{httr}`, `{rlist}`, `{jsonlite}` and
`{tidyverse}`. For the visualization of the extracted data in task 5, the 
package `{maps}` is needed.

To ensure reusability of the code, the functions `first.quest(country, key)`, 
which performs the first `GET` request, and `first.df(venues, content_venues)`,
which creates a data frame based on the response of a `GET` request, have been 
implemented.

```{r functions1, include = FALSE, echo = FALSE}

first.quest <- function(country, key) {
  # Gets the response from Ticketmaster.com and returns it
  venues <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                query = list(locale = "*",
                             countryCode = country,
                             apikey = key))
  venues
}

first.df <- function(venues, content_venues) {
  # Processes the response from Ticketmaster.com
  json_parsed_search <- fromJSON(content(venues, as = "text"))[["_embedded"]][["venues"]]
  
  n = as.numeric(content_venues$page$size)
  
  venue_data <-
    data.frame(
      name = character(n),
      city = character(n),
      postalCode = character(n),
      address = character(n),
      url = character(n),
      longitude = double(n),
      latitude = double (n)
    )
  
  venue_data[, 1] <- json_parsed_search$name
  venue_data[, 2] <- json_parsed_search$city$name
  venue_data[, 3] <- json_parsed_search$postalCode
  venue_data[, 4] <- json_parsed_search$address$line1
  venue_data[, 5] <- json_parsed_search$url
  venue_data[, 6] <- as.double(json_parsed_search$location$longitude)
  venue_data[, 7] <- as.double(json_parsed_search$location$latitude)
  
  venue_data
}
```

`country` is set to the country code of Germany, `"DE"`, and will be used for 
the following tasks.

With that, the command for the first `GET` request for venues in Germany takes
the following form:

```{r analysisDE1, echo = TRUE}

country <- "DE"

response_1 <- first.quest(country, tm_key)
content_1 <- content(response_1)

venue_data_1 <- first.df(response_1, content_1)

glimpse(venue_data_1)
``` 

The status of the response is `r status_code(response_1)`, which indicates the
success of the request. 
`content()`  delivers a list of length `r length(content_1)` that supports 
on understanding the data. 
The element `_embedded` contains the 
`r length(content_1$'_embedded'$venues)` venues, that are returned. 
The element `links` contains pointers to the current page as well as to the 
first, the next and the last one. The element `page` specifies the response: 
the returned page consists of `r content_1$page$size` items, in total there are 
`r content_1$page$totalElements` elements that are stored on 
`r content_1$page$totalPages` pages.

From trying to set `size = 12238`, we receive the message, that the spezified 
size of elements must not exceed 500.

## 4 Interacting with the API - advanced

The request from task 3 did not return all event locations in Germany. As stated
in the list element `page`, the total number of venues is
`r content_1$page$totalElements`.

The pages can be iterated by using the parameter `page` in the `GET` request.
This parameter starts by default at the value `0`.

In order to adjust the returned number of elements per page, the function 
`second.quest(country, size, key)` takes the additional parameter `size`.
To determine the number of pages, a first `GET` request is performed and the 
number of resulting pages can be extracted. This value is used in a `for` loop 
that iterates through the pages. 

Since the API sets a a rate limitation of 5 requests per second, 
`Sys.sleep(time)` is used to avoid sending more than 5 requests per second. 
While working on the task, it appeared that `Sys.sleep(0.2)` leads to a problem
in filling the data frame properly. If this problem occurs, it can solved by 
setting `time = 0.4`.

Further, the data frame that stores the extracted data is initialized directly
from the information of the first request.

```{r functions2, echo = FALSE, include = FALSE}

second.quest <- function(country, size, key){

  venues <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                query = list(locale = "*",
                             size = size,
                             countryCode = country,
                             apikey = key))
  
  content_venues <- content(venues)
  
  n = as.numeric(content_venues$page$totalElements)
  l = as.numeric(content_venues$page$totalPages)
  
  venue_data <-
    data.frame(
      name = character(n),
      city = character(n),
      postalCode = character(n),
      address = character(n),
      url = character(n),
      longitude = double(n),
      latitude = double (n)
    )
  
  for (i in 1:l){
    venues <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                query = list(locale = "*",
                             size = size,
                             countryCode = country,
                             apikey = key,
                             page = i-1))
    json_parsed_search <- fromJSON(content(venues, as = "text"))[["_embedded"]][["venues"]]
    
    rows <- as.numeric(nrow(json_parsed_search))
    
    if (i == l) {
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 1] <- json_parsed_search$name
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 2] <- json_parsed_search$city$name
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 3] <- json_parsed_search$postalCode
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 4] <- json_parsed_search$address$line1
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 5] <- json_parsed_search$url
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 6] <- as.double(json_parsed_search$location$longitude)
      venue_data[((i-1)*size + 1):((i-1)*size + rows), 7] <- as.double(json_parsed_search$location$latitude)
    } else {
      venue_data[((i-1)*size + 1):(i*rows), 1] <- json_parsed_search$name
      venue_data[((i-1)*size + 1):(i*rows), 2] <- json_parsed_search$city$name
      venue_data[((i-1)*size + 1):(i*rows), 3] <- json_parsed_search$postalCode
      venue_data[((i-1)*size + 1):(i*rows), 4] <- json_parsed_search$address$line1
      venue_data[((i-1)*size + 1):(i*rows), 5] <- json_parsed_search$url
      venue_data[((i-1)*size + 1):(i*rows), 6] <- as.double(json_parsed_search$location$longitude)
      venue_data[((i-1)*size + 1):(i*rows), 7] <- as.double(json_parsed_search$location$latitude)
    }
  
    Sys.sleep(0.2)
  }
  venue_data
}
```

By calling `second.quest(country, size, key)` to obtain all venues in Germany, 
the following result is obtained:
```{r analysisDE2, echo = TRUE, include = TRUE}

# The parameter "size" can take a maximum value of 500
venue_data_2 <- second.quest(country, 500, tm_key)

glimpse(venue_data_2)
``` 

## 5 Visualizing the extracted data

For the visualization, the function 
`visualization(venue_data, long_min, long_max, lat_min, lat_max, country)` has 
been implemented. Prior to the mapping, all values that lie beyond the German 
borders are set to `NA`. Therefore, the parameters `long_min`, `long_max`, 
`lat_min` and `lat_max` determine the borders that must not be exceeded.

For the creation of the plot, the parameter `country` is used to specify the 
visualized country, but must not be confused with the country code that has
been used before.

To ensure reusability in the following task, the given code has been adjusted,
such that it is possible to run the function for different countries.

```{r functions3, echo = FALSE, include = FALSE}

visualization <- function(venue_data, long_min, long_max, lat_min, lat_max, country){
  n <- nrow(venue_data)
  
  # Set the values for longitude and latitude that lie outside the boundaries of 
  # a country to NA
  for (i in 1:n){
    if ((is.na(venue_data$longitude[i])) | (is.na(venue_data$latitude[i]))){
    
    } else if((venue_data[i, 6] < long_min) |
              (venue_data[i, 6] > long_max) | 
              (venue_data[i, 7] < lat_min) |
              (venue_data[i, 7] > lat_max)){
                venue_data[i, 6] <- NA
                venue_data[i, 7] <- NA
    }
  }
  
  cap = paste("Event locations across", country)
  vis <- ggplot() + 
          geom_polygon(
            aes(x = long, y = lat, group = group), data = map_data("world", region = country),
            fill = "grey90", color = "black") + 
          theme_void() + coord_quickmap() + 
          labs(title = cap, 
               caption = "Source: ticketmaster.com") + 
          theme(title = element_text(size = 8, face = 'bold'),
                plot.caption = element_text(face = "italic")) + 
                geom_point(aes(x = longitude, y = latitude), data = venue_data,
                           na.rm = TRUE)
  # NA-values are silently removed
  vis
}
```

With these adjustment, the following plot indicates the locations of the event
venues across Germany:

```{r visualizationDE, echo = TRUE, include = TRUE}

region = "Germany"

plot_1 <- visualization(venue_data_2, 5.866944, 15.043611, 47.271679, 55.0846, region)
plot_1
```

## 6 Event locations in other countries

To see the event locations across the Netherlands, the prior functions are 
reused with new parametrizations. 
Therefore, `country` is now set to `"NL"`.

The rules for using the API remain unchanged with a maximum of 5000 API calls 
per day with a rate limitation of 5 requests per second.

A first quest for the event venues across the Netherlands yields the following
result:
```{r analysisNL1}

# Task 2 and 3
country = "NL"

response_2 <- first.quest(country, tm_key)
content_2 <- content(response_2)

venue_data_3 <- first.df(response_2, content_2)

glimpse(venue_data_3)
``` 

The status of the response is `r status_code(response_2)`, which indicates the
success of the request. 
`content()`  delivers a list of length `r length(content_2)` that supports on 
understanding the data. 
The element `_embedded` contains the `r length(content_2$'_embedded'$venues)` 
venues, that are returned. 
The element `links` contains pointers to the current page as well as to the 
first, the next and the last page. 
The element `page` specifies the response: 
the returned page consists of `r content_2$page$size` items, in total there are 
`r content_2$page$totalElements` elements that are stored on 
`r content_2$page$totalPages` pages.

The maximum of `500` elements per page does still hold. So, `size = 500` in the
function call.

Reusing `second.quest(country, size, key)` with the adjusted parametrization
yields the following result:

```{r analysisNL2}

# Task 4
venue_data_4 <- second.quest(country, 500, tm_key)

glimpse(venue_data_4)
```

The values that determine the borders of the Netherlands have been derived from
the extreme points of the Netherlands as listed on 
[Wikipedia](https://en.wikipedia.org/wiki/List_of_extreme_points_of_the_Netherlands).

The plot of the event venues across the Netherlands is displayed in the 
following:

```{r analysisNL3}

# Task 5
region = "Netherlands"

# Northernmost point in sea, but identical results
plot_2 <- visualization(venue_data_4, 3.358333, 7.227778, 50.750417, 53.555, region)
plot_2
```